Global patterns of forest autotrophic carbon fluxes

### 2019-11-14 manuscript/manuscript draft.Rmd
minor change to table2

| Variable | Definition | Components included | Methodologies used | Number of records | Number of geographic areas |
|--------------|-------------------|-------------|------------------------|-------|-------|
| $GPP$ | Annual gross primary production; annual uptake of carbon dioxide by an ecosystem | NA | Flux partitioning of eddy covariance | 243 | 49 |
| $NPP$ | Annual net primary production; the component of GPP that is stored in plant tissue; $GPP - R_{auto}$ | Foliage, branch, stem, coarse root and fine root | Direct measurement of annual increments of components | 92 | 42 |
| $ANPP$ | Aboveground net primary production | Foliage, stem, and optionally branch | Direct measurement of annual increments of components | 256 | 80 |
| $ANPP_{foliage}$ | Net primary production of foliage | Foliage | Direct measurement of litterfall, correcting for changes in leaf biomass when measured | 98 | 49 |
| $ANPP_{woody-stem}$ | Net primary production of woody stems | Woody stems | Direct measurement of stem growth increment | 264 | 96 |
| $BNPP_{root}$  | Belowground net primary production | Coarse and fine roots |  indirect estimates of coarse roots using allometries based on aboveground stem increment measures ; see below for fine roots | 101 | 48 |
| $BNPP_{fine.root}$ | Net primary production of fine roots | Fine roots | Measurements combined one or more of the following: minirhizotrons, fine root turnover, soil cores, root ingrowth cores | 88 | 41 |
| $R_{auto}$ | Annual autotrophic respiration, including above- and belowground components | Foliage, stem, and root | Chamber measurements of component gas exchange | 22 | 13 |
| $R_{root}$ | Annual root respiration | Coarse and fine roots | *Measurement of root gas exchange, root exclusion from soil respiration chambers* | 64 | 26 |

>>>>

| Variable | Definition | Components included | Methodologies used | Number of records | Number of geographic areas |
|--------------|-------------------|-------------|------------------------|-------|-------|
| $GPP$ | Annual gross primary production; annual uptake of carbon dioxide by an ecosystem | NA | Flux partitioning of eddy covariance | 243 | 49 |
| $NPP$ | Annual net primary production; the component of GPP that is stored in plant tissue; $GPP - R_{auto}$ | Foliage, branch, stem, coarse root and fine root | Direct measurement of annual increments of components | 92 | 42 |
| $ANPP$ | Aboveground net primary production | Foliage, stem, and optionally branch | Direct measurement of annual increments of components | 256 | 80 |
| $ANPP_{foliage}$ | Net primary production of foliage | Foliage | Direct measurement of litterfall, correcting for changes in leaf biomass when measured | 98 | 49 |
| $ANPP_{woody-stem}$ | Net primary production of woody stems | Woody stems | Direct measurement of stem growth increment | 264 | 96 |
| $BNPP_{root}$  | Belowground net primary production | Coarse and fine roots |  Coarse roots estimated indirectly using allometries based on aboveground stem increment measures ; fine roots as below | 101 | 48 |
| $BNPP_{fine.root}$ | Net primary production of fine roots | Fine roots | Measurements combined one or more of the following: minirhizotrons, fine root turnover, soil cores, root ingrowth cores | 88 | 41 |
| $R_{auto}$ | Annual autotrophic respiration, including above- and belowground components | Foliage, stem, and root | Chamber measurements of component gas exchange | 22 | 13 |
| $R_{root}$ | Annual root respiration | Coarse and fine roots | *Measurement of root gas exchange, root exclusion from soil respiration chambers* | 64 | 26 |
